---
title: "my title"

author: 
  - name: Christine Iyer
    affiliation: ebd
    email: youremail(at)gmail.com
    footnote: Corresponding author
    
  - name: First Coauthor 
    affiliation: shortcode

address: 
  - code: ebd
    address: institution, address, postcode and country 
  - code: shortcode
    address: Full address of First Coauthor

documentclass: elsarticle

output: 
  pdf_document:
    template: elsarticle.latex
    keep_tex: yes
    fig_caption: yes
    toc: false
    
bibliography: references.bib
csl: ecology.csl

abstract: | 
          Write the abstract of the paper here
          
---

<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Example Manuscript}
-->


```{r knitr_setup, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}

library(rmarkdown)
library(knitr)
library(dplyr)
library(salesforcer)
library(knitr)
library(RForcecom)
library(tidyr)
library(tinytex)

### Chunk options ###

# Modify at your will #


## Text results
opts_chunk$set(echo = TRUE, warning=TRUE, message=TRUE)

## Code decoration
opts_chunk$set(tidy=TRUE, comment = NA, highlight = TRUE)

## Cache
opts_chunk$set(cache = 2, cache.path = "output/cache/")
opts_chunk$set(cache.extra = rand_seed)

## Plots
opts_chunk$set(fig.path = "output/figures/")
opts_chunk$set(dpi = 300, fig.align = "default")   # may want 'center' sometimes

# Figure format
opts_chunk$set(dev='png')  # e.g. choose among 'pdf', 'png', 'svg'...
# may include specific dev.args as a list... see knitr help


```


```{r citations_setup, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}

library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")

if (file.exists("refs2import.bib")) 
  refs <- read.bibtex("refs2import.bib", check=FALSE)

```



# November 2019 





```{r echo=FALSE, message=FALSE, warning=FALSE}
queried_records <- read.csv("C:/Users/christine.iyer/Box/GeneralPurposeSearch/SF_Requests/FYNovember.csv", header = T, stringsAsFactors = F)

LeadsUploaded <- read.csv("file:///C:/Users/christine.iyer/Desktop/Fall19Leads/Fall2019LeadsafterUploadAndDeDuped.csv", header = T, stringsAsFactors = F)
```



```{r echo=FALSE, message=FALSE, warning=FALSE}
trythis <- merge(LeadsUploaded, queried_records, by = "Email" )
trythis <- trythis %>% mutate(DateCollected = Sys.Date())
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#trythis
# Don't forget to change the data!

write.csv(trythis, "file:///C:/Users/christine.iyer/Box/Search/FY20_Search/FY20_November_Search/Conversions Fall 2020/Conversion_06-10-20_DeDuped.csv")
```

### Conversion Summary as of `r Sys.Date()`

```{r echo=FALSE, message=FALSE, warning=FALSE}
trythisGrouped <- trythis %>% mutate(
  Vendor = ifelse(grepl('^N', Recruiting.Category), 'NRCCUA', 'College Board'),
   Class = ifelse(grepl('SR', Recruiting.Category), 'Senior', 'Junior') ,
    Geo = ifelse(grepl('O', Recruiting.Category), 'Out-of_State', 'In-State'))


trythisGroupedStatus <- trythisGrouped %>% group_by(Vendor, Class, Geo,
                                                    TargetX_SRMb__Status__c) %>% summarise(n = n())



trythisGroupedStatus <- trythisGroupedStatus %>% spread(TargetX_SRMb__Status__c, n) %>% mutate_at(4:5, ~replace(., is.na(.), 0))

trythisGroupedStatus <- trythisGroupedStatus %>%
  group_by(Vendor, Class, Geo) %>% 
  summarise(
  Inquiry = (sum(Inquiry) + sum(Applicant)), 
  Applicant = sum(Applicant))

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
LeadsUploaded <- LeadsUploaded %>% 
  mutate(
  Vendor = ifelse(grepl('^N', Recruiting.Category), 'NRCCUA', 'College Board'),
   Class = ifelse(grepl('SR', Recruiting.Category), 'Senior', 'Junior'),
  Geo = ifelse(grepl('O', Recruiting.Category), 'Out-of_State', 'In-State')) %>% 
  group_by(Geo,Class, Vendor
           ) %>% summarise(Leads = n())
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
nwew <- left_join(LeadsUploaded, trythisGroupedStatus)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
nwew <- nwew %>% 
  mutate(Inquiry_Yield = 
          paste0(round(Inquiry/Leads * 100,2), "%"),
         App_Yield = 
          paste0(round(Applicant/Leads * 100,2), "%")) 
         
```


**In-State Senior**

```{r echo=FALSE, message=FALSE, warning=FALSE}
kable(nwew %>% filter(Geo == "In-State" & Class == "Senior"))
```

**Out-of-State Senior **

```{r echo=FALSE, message=FALSE, warning=FALSE}
kable(nwew %>% filter(Geo == "Out-of_State" & Class == "Senior"))
```

**In-State Junior**

```{r echo=FALSE, message=FALSE, warning=FALSE}
kable(nwew %>% filter(Geo == "In-State" & Class == "Junior") %>% 
        select(Geo:Inquiry_Yield))
```

**Out-of_State Junior**

```{r echo=FALSE, message=FALSE, warning=FALSE}
kable(nwew %>% filter(Geo == "Out-of_State" & Class == "Junior") %>% 
        select(Geo:Inquiry_Yield))
```




 


#January Senior


```{r}
library(dplyr)
queried_records_Jan_SR <- read.csv("C:/Users/christine.iyer/Box/GeneralPurposeSearch/SF_Requests/FYJanSR.csv", header = T, stringsAsFactors = F)

queried_records_Jan_SR <- queried_records_Jan_SR %>%
  mutate(Geo = ifelse(Primary_State_Code__c == "ME", "In-State", "Out-of-State")) %>% filter(TargetX_SRMb__Anticipated_Start_Year__c == 2020)

LeadsUploaded <- read.csv("C:/Users/christine.iyer/Box/Search/FY20_Search/FY20_January_Search/FA20_Senior/FA20_Search_Jan2020_SR.csv", header = T, stringsAsFactors = F)
Leads <- LeadsUploaded %>% 
  mutate(Geo = ifelse(Primary.State.Province == "Maine", "In-State", "Out-of-State"), 
         Vendor = ifelse(Lead.Segment.NRCCUA == "", "CB", 
                         ifelse(Lead.Segment.College.Board == "", "NRCCUA", "Both"))) %>% 
  group_by(Geo, Vendor) %>% 
  summarise(Leads = n())
trythis <- merge(LeadsUploaded, queried_records_Jan_SR, by = "Email" )
trythis <- trythis %>% mutate(DateCollected = Sys.Date(), 
                              Vendor = ifelse(Lead.Segment.NRCCUA == "", "CB", 
                         ifelse(Lead.Segment.College.Board == "", "NRCCUA", "Both")))

# Don't forget to change the date!
# Don't forget to change the date!
# Don't forget to change the date!

write.csv(trythis,"C:/Users/christine.iyer/Box/Search/FY20_Search/FY20_Combined_Search_Feb_March/Senior_Conversions/Conversions_6-10-20_DeDuped", row.names = F)
```

```{r}
trythisGroup <- trythis %>% group_by(Geo, Vendor, TargetX_SRMb__Status__c) %>% summarise(n = n()) %>% spread(TargetX_SRMb__Status__c,n) 
trythisGroup$Inquiry[is.na(trythisGroup$Inquiry)] <- 0
trythisGroup <- trythisGroup %>% mutate(Inquiry = sum(Applicant) + sum(Inquiry)) %>% select(Geo, Vendor, Inquiry, Applicant)
SRConversion <- left_join(Leads,trythisGroup %>% group_by(Geo, Vendor) %>% summarise(Inquiries = sum(Inquiry), Applicants = sum(Applicant)))
SRConversion$Inquiries[is.na(SRConversion$Inquiries)] <- 0
SRConversion$Applicants[is.na(SRConversion$Applicants)] <- 0
kable(SRConversion %>% mutate(Inquiry_Yield = 
          paste0(round(Inquiries/Leads * 100,2), "%"),
         App_Yield = 
          paste0(round(Applicants/Leads * 100,2), "%")))
```


# January Juniors 

```{r}
queried_records_JR <- read.csv("C:/Users/christine.iyer/Box/GeneralPurposeSearch/SF_Requests/queriedRecords_JUNIOR.csv", header = T, stringsAsFactors = F)

queried_records_JR <- queried_records %>%
  mutate(Geo = ifelse(Primary_State_Code__c == "ME", "In-State", "Out-of-State")) 

LeadsUploaded_JR <- read.csv("C:/Users/christine.iyer/Box/Search/FY20_Search/FY20_Combined_Search_Feb_March/FY20_Feb_Search_Upload_DeDuped.csv", header = T, stringsAsFactors = F)

LeadsUploaded_JR <- LeadsUploaded_JR %>% filter(Anticipated.Start.Year == 2021)

trythis_JR <- merge(LeadsUploaded_JR, queried_records_JR, by = "Email" )




trythis_JR <- trythis_JR %>% mutate(DateCollected = Sys.Date(), 
                              Vendor = ifelse(Lead.Segment.NRCCUA == "", "CB", 
                         ifelse(Lead.Segment.College.Board == "", "NRCCUA", "Both")))
LeadsUploaded_JR <- LeadsUploaded_JR %>% 
  mutate(Geo = ifelse(Primary.State.Province == "Maine", "In-State", "Out-of-State"), 
         Vendor = ifelse(Lead.Segment.NRCCUA == "", "CB", 
                         ifelse(Lead.Segment.College.Board == "", "NRCCUA", "Both"))) %>% 
  group_by(Geo, Vendor) %>% 
  summarise(Leads = n())


trythisGroup_JR <- trythis_JR %>% group_by(Geo, Vendor, TargetX_SRMb__Status__c) %>% summarise(n = n()) %>% spread(TargetX_SRMb__Status__c,n) 
trythisGroup_JR$Applicant[is.na(trythisGroup_JR$Applicant)] <- 0
trythisGroup_JR <- trythisGroup_JR %>% mutate(Inquiry = sum(Applicant) + sum(Inquiry)) %>% select(Geo, Vendor, Inquiry, Applicant)
trythisGroup_JR <- trythisGroup_JR[c(1:6),]
JRConversion_JR <- left_join(LeadsUploaded_JR,trythisGroup_JR %>% group_by(Geo, Vendor) %>% summarise(Inquiries = sum(Inquiry), Applicants = sum(Applicant)))
JRConversion_JR$Inquiries[is.na(JRConversion_JR$Inquiries)] <- 0
JRConversion_JR$Applicants[is.na(JRConversion_JR$Applicants)] <- 0
kable(JRConversion_JR %>% mutate(Inquiry_Yield = 
          paste0(round(Inquiries/Leads * 100,2), "%"),
         App_Yield = 
          paste0(round(Applicants/Leads * 100,2), "%")))
```


# January Sophomores




```{r}

queried_records_PH <- read.csv("C:/Users/christine.iyer/Box/GeneralPurposeSearch/SF_Requests/queriedRecords_SOPHOMORE.csv", header = T, stringsAsFactors = F)



queried_records_PH <- queried_records_PH %>%
  mutate(Geo = ifelse(Primary_State_Code__c == "ME", "In-State", "Out-of-State")) 

LeadsUploaded_PH <- read.csv("C:/Users/christine.iyer/Box/Search/FY20_Search/FY20_Combined_Search_Feb_March/FY20_Feb_Search_Upload_DeDuped.csv", header = T, stringsAsFactors = F)
LeadsUploaded_PH <- LeadsUploaded_PH %>% filter(Anticipated.Start.Year >2021)

trythis_PH <- merge(queried_records_PH, LeadsUploaded_PH, by = "Email" )




trythis_PH <- trythis_PH %>% mutate(DateCollected = Sys.Date(), 
                              Vendor = ifelse(Lead.Segment.NRCCUA == "", "CB", 
                         ifelse(Lead.Segment.College.Board == "", "NRCCUA", "Both")))
LeadsUploaded_PH <- LeadsUploaded_PH %>% 
  mutate(Geo = ifelse(Primary.State.Province == "Maine", "In-State", "Out-of-State"), 
         Vendor = ifelse(Lead.Segment.NRCCUA == "", "CB", 
                         ifelse(Lead.Segment.College.Board == "", "NRCCUA", "Both"))) %>% 
  group_by(Geo, Vendor) %>% 
  summarise(Leads = n())


trythisGroup_PH <- trythis_PH %>% group_by(Geo, Vendor, TargetX_SRMb__Status__c) %>% summarise(n = n()) 
Conversion_PH <- left_join(LeadsUploaded_PH,trythisGroup_PH %>% group_by(Geo, Vendor) %>% summarise(Inquiries = sum(n)))
Conversion_PH$Inquiries[is.na(Conversion_PH$Inquiries)] <- 0
# JRConversion_JR$Applicants[is.na(JRConversion_JR$Applicants)] <- 0
kable(Conversion_PH %>% mutate(Inquiry_Yield = 
          paste0(round(Inquiries/Leads * 100,2), "%"),
         ))
```

# April Juniors

```{r}

queried_records_PH <- read.csv("C:/Users/christine.iyer/Box/GeneralPurposeSearch/SF_Requests/April_queriedRecords_JUNIOR.csv", header = T, stringsAsFactors = F)



queried_records_PH <- queried_records_PH %>%
  mutate(Geo = ifelse(Primary_State_Code__c == "ME", "In-State", "Out-of-State")) 

LeadsUploaded_PH <- read.csv("C:/Users/christine.iyer/Box/Search/FY20_Search/FY20_April_Search/SF_Downloaded_Names/AprilSearchDownload.csv", header = T, stringsAsFactors = F)
LeadsUploaded_PH <- LeadsUploaded_PH %>% filter(Anticipated.Start.Year == 2021)

trythis_PH <- merge(queried_records_PH, LeadsUploaded_PH, by = "Email" )


trythis_PH <- trythis_PH %>% mutate(DateCollected = Sys.Date(),
                                    Vendor = ifelse(Lead.Segment.NRCCUA == "", "CB",
                                              ifelse(Lead.Segment.College.Board == "", "NRCCUA", "Both")))
LeadsUploaded_PH <- LeadsUploaded_PH %>% 
  mutate(Geo = ifelse(Primary.State.Province == "Maine", "In-State", "Out-of-State"), 
         Vendor = ifelse(Lead.Segment.NRCCUA == "", "CB", 
                         ifelse(Lead.Segment.College.Board == "", "NRCCUA", "Both"))) %>% 
  group_by(Geo, Vendor) %>% 
  summarise(Leads = n())


trythisGroup_PH <- trythis_PH %>% group_by(Geo, Vendor, TargetX_SRMb__Status__c) %>% summarise(n = n()) 
Conversion_PH <- left_join(LeadsUploaded_PH,trythisGroup_PH %>% group_by(Geo, Vendor) %>% summarise(Inquiries = sum(n)))
Conversion_PH$Inquiries[is.na(Conversion_PH$Inquiries)] <- 0
# JRConversion_JR$Applicants[is.na(JRConversion_JR$Applicants)] <- 0
kable(Conversion_PH %>% mutate(Inquiry_Yield = 
          paste0(round(Inquiries/Leads * 100,2), "%"),
         ))
```

# April Sophomores

```{r}

queried_records_PH <- read.csv("C:/Users/christine.iyer/Box/GeneralPurposeSearch/SF_Requests/April_queriedRecords_SOPHOMORE.csv", header = T, stringsAsFactors = F)



queried_records_PH <- queried_records_PH %>%
  mutate(Geo = ifelse(Primary_State_Code__c == "ME", "In-State", "Out-of-State")) 

LeadsUploaded_PH <- read.csv("C:/Users/christine.iyer/Box/Search/FY20_Search/FY20_April_Search/SF_Downloaded_Names/AprilSearchDownload.csv", header = T, stringsAsFactors = F)
LeadsUploaded_PH <- LeadsUploaded_PH %>% filter(Anticipated.Start.Year >2021)

trythis_PH <- merge(queried_records_PH, LeadsUploaded_PH, by = "Email" )


trythis_PH <- trythis_PH %>% mutate(DateCollected = Sys.Date(),
                                    Vendor = ifelse(Lead.Segment.NRCCUA == "", "CB",
                                              ifelse(Lead.Segment.College.Board == "", "NRCCUA", "Both")))
LeadsUploaded_PH <- LeadsUploaded_PH %>% 
  mutate(Geo = ifelse(Primary.State.Province == "Maine", "In-State", "Out-of-State"), 
         Vendor = ifelse(Lead.Segment.NRCCUA == "", "CB", 
                         ifelse(Lead.Segment.College.Board == "", "NRCCUA", "Both"))) %>% 
  group_by(Geo, Vendor) %>% 
  summarise(Leads = n())


trythisGroup_PH <- trythis_PH %>% group_by(Geo, Vendor, TargetX_SRMb__Status__c) %>% summarise(n = n()) 
Conversion_PH <- left_join(LeadsUploaded_PH,trythisGroup_PH %>% group_by(Geo, Vendor) %>% summarise(Inquiries = sum(n)))
Conversion_PH$Inquiries[is.na(Conversion_PH$Inquiries)] <- 0
# JRConversion_JR$Applicants[is.na(JRConversion_JR$Applicants)] <- 0
kable(Conversion_PH %>% mutate(Inquiry_Yield = 
          paste0(round(Inquiries/Leads * 100,2), "%"),
         ))
```


__Junior__

# June (Cappex)

```{r}
CappexNames <- read.csv("C:/Users/christine.iyer/Box/Cappex Leads FY20/FY20CappexLeads.csv", header = T, stringsAsFactors = F)
```


```{r}
library(dplyr)
names(CappexNames)
states <- c("ME", "NH", "MA", "CT")
CappexNames %>% 
  mutate(StateRegion = ifelse(State %in% states, "New England", "Outside NE")) %>% 
  group_by(StateRegion,State) %>% summarise(n = n())
```


__Sophomores__

__Junior__






Rmarkdown is great `r citep(citation("knitr"))`. 

You can write all your R code in chunks here and the output will appear in the final document. For example:

```{r test, echo=FALSE, cache=FALSE}
cat("Hello world!")
```

# 
You can import references from a BibTeX file and cite any of them like these: `citep(refs["Xie_2013"])`. Or cite by doi, e.g. `r citet("10.1098/rspb.2013.1372")`, thanks to `knitcitations` package `r citep(citation("knitcitations"))`. 

You can even specifiy the desired format for your bibliography by including a style file ("bibliostyle.csl"). See [Rstudio website](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html) for more help. You can grab many different bibliography styles here: http://citationstyles.org/.

There is a chunk in the end to provide your session info at the end of the document (useful for reproducibility). Set eval=FALSE if you don't want to include that info in your document.


```{r sessionInfo, cache=FALSE, echo=FALSE, eval=FALSE}
devtools::sessionInfo()
```


## References

```{r generate_references, cache=FALSE, include=FALSE, results='hide'}
write.bibtex(file="references.bib", 
             append=file.exists("references.bib"))

```
